### 2018-09-10 introduction.tex
Lit review words fixed #25

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
material moves to and from the core continuously or at specific time steps 
(batch-wise). In the batch-wise approach, the burn-up simulation stops at a given 
time and restarts with a new liquid fuel composition (after removal of discarded 
materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
batch-wise approach to simulate a continuous reprocessing. ChemTriton models salt 
treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
SCALE/TRITON depletion simulation over small time steps to simulate continuous 
reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, 
jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
as well as the current work employ a batch-wise approach.

Accounting for continuous removal or addition presents a greater challenge since it 
requires adding a term to the Bateman equations. In SCALE 
\cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of 
Bateman equations using spectrum-averaged fluxes and cross sections generated 
from a deterministic transport calculation. Meanwhile, approaches listed in references 
\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} 
model true continuous feeds and removals.

>>>>

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
material moves to and from the core continuously or at specific time steps 
(batch-wise). In the batch-wise approach, the burn-up simulation stops at a given 
time and restarts with a new liquid fuel composition (after removal of discarded 
materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
batch-wise approach to simulate a continuous reprocessing. ChemTriton models salt 
treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
SCALE/TRITON depletion simulation over small time steps to simulate continuous 
reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, 
jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
as well as the current work also employ a batch-wise approach.

Accounting for continuous removal or addition presents a greater challenge since it 
requires adding a term to the Bateman equations. Aufiero \emph{et al.} explicitly
introduced online fuel reprocessing in the system of equations by adding effective 
decay and transmutation terms for the different nuclides. In his work SERPENT was 
used for solution of the matrix exponential derived from the system of the Bateman 
equations \cite{aufiero_extended_2013}. Similar approach is adopted to model true 
continuous feeds and removals using MCNP transport code listed in references 
\cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.
